---
title: "TIME SERIES ANALYSES OF EYETRACKING DATA"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
# Index

| Section | Description | Status |
| --- | --- | --- |
| [Window Analysis](#windowan) | Standard AOI analysis (no time dimension) | **Complete** |
| [Growth Curve Analysis](#growthcurve) | Model change in gaze bias over time | **Complete** |
| [Divergence Analysis](#divergence) | Apply tests to determine when predictors had an effect | **Complete** |
| [Switching Analysis](#switching) | Model swtiches from one AOI to another | **Complete** |
| [Individual differences](#indiff) | Look at relationship between individual random effects and EQ data | Incomplete |

Still to do:

1. Individual differences / EQ .
2. Classification of time-series (python).

***


## Import data into eyetrackingR format and add factors

```{r}
load('Workspace3.RData')
library(eyetrackingR)
data <- make_eyetrackingr_data(EXPDATA_FRAME_BIG, 
                               participant_column = "ps",
                               trial_column = "trial",
                               time_column = "samp",
                               aoi_columns = c('isinL','isinR',"SOCIAL","NONSOCIAL"),
                               treat_non_aoi_looks_as_missing = TRUE,trackloss_column="track")

data$scramb=factor(data$scramb)
data$X3=factor(data$X3,levels=c(1,2),labels=c("LeftSoc","Rightsoc"))
```

***

<a id='windowan'></a>

## Window analysis_plot
```{r}
library(ggplot2)
response_window_agg_by_sub <- make_time_window_data(data, aois=c("SOCIAL","NONSOCIAL"),summarize_by = "ps",predictor_columns = c("scramb"))

plot(response_window_agg_by_sub, predictor_column = "scramb")+geom_point(aes(colour=ps),position = position_jitter(w=0.3))

```

## Window analysis_model
```{r}
library(lme4)
library(afex)
library(phia)
library(nlme)
library(effects)
# Set up model
model_window <- lmer(Prop ~ AOI*scramb + (1 | ps), data = response_window_agg_by_sub, REML = FALSE)

model_window_p = mixed(Prop ~ AOI*scramb+(1|ps), response_window_agg_by_sub)

# Get p values
model_window_p

# Test interactions
testInteractions(model_window, fixed=c("scramb"), pairwise=c("AOI"),adjustment="holm")

```

There are main effects of AOI and an interaction between AOI and scramb. The effect of AOI is greater in the intact condition.

***
<a id='growthcurve'></a>

## Growth Curve analysis_plot

```{r}
response_time <- make_time_sequence_data(data, time_bin_size = 100,aois = c("NONSOCIAL","SOCIAL"),summarize_by = "ps",predictor_columns = c("scramb"))

plot(response_time, predictor_column = "scramb")
```


## Growth Curve analysis_model

Since we are dealing with mutliple interactions with multiple higher-order polynomials, I think it is justified to fit a model independently to scrambled and intact stimuli, to improve interpretation.

### Intact
```{r}
# Just AOI factor
model_time_sequence_intact1 <- lmer(Prop ~ AOI+(1|ps),data = response_time[response_time$scramb==1,], REML = FALSE)
# Linear
model_time_sequence_intact2 <- lmer(Prop ~ AOI*(ot1)+(1 + ot1 |ps),data = response_time[response_time$scramb==1,], REML = FALSE)
# Linear + quadratic
model_time_sequence_intact3 <- lmer(Prop ~ AOI*(ot1+ot2)+(1 + ot1 + ot2 |ps),data = response_time[response_time$scramb==1,], REML = FALSE)
# Linear + quadratic + cubic
model_time_sequence_intact4 <- lmer(Prop ~ AOI*(ot1+ot2+ot3)+(1+ ot1 + ot2 + ot3 |ps),data = response_time[response_time$scramb==1,], REML = FALSE)

anova(model_time_sequence_intact1,model_time_sequence_intact2)
anova(model_time_sequence_intact2,model_time_sequence_intact3)
anova(model_time_sequence_intact3,model_time_sequence_intact4)
```


This indicates that best fitting model is linear + quadratic - so check that a model with just the quadratic component isn't better

```{r}
model_time_sequence_intact5 <- lmer(Prop ~ AOI*(ot2)+(1 + ot2|ps),data = response_time[response_time$scramb==1,], REML = FALSE)

anova(model_time_sequence_intact3,model_time_sequence_intact5)
```


Model 3 is best fitting, so plot this.


```{r}
plot(response_time[response_time$scramb==1,], predictor_column = c("AOI"), dv = "Prop", model = model_time_sequence_intact3) +theme_light()
```

### Scrambled

```{r}
# AOI
model_time_sequence_scramb1 <- lmer(Prop ~ AOI+(1|ps),data = response_time[response_time$scramb==2,], REML = FALSE)
# AOI + linear
model_time_sequence_scramb2 <- lmer(Prop ~ AOI*(ot1)+(1 +ot1| ps),data = response_time[response_time$scramb==2,], REML = FALSE)
# AOI + linear + quadratic
model_time_sequence_scramb3 <- lmer(Prop ~ AOI*(ot1+ot2)+(1 + ot1 + ot2 |ps),data = response_time[response_time$scramb==2,], REML = FALSE)

anova(model_time_sequence_scramb1,model_time_sequence_scramb2)
anova(model_time_sequence_scramb1,model_time_sequence_scramb3)
```


Linear + quadratic improves - but linear itself did not - is quadratic better than linear + quadratic?


```{r}
model_time_sequence_scramb4 <- lmer(Prop ~ AOI*(ot2)+(1|ps),data = response_time[response_time$scramb==2,], REML = FALSE)
anova(model_time_sequence_scramb4,model_time_sequence_scramb3)
```


Yes it is, so model 4 is best fitting (cubic term, but no linear term)


```{r}
plot(response_time[response_time$scramb==2,], predictor_column = c("AOI"), dv = "Prop", model = model_time_sequence_scramb4) +theme_light()
```

***

<a id='divergence'></a>

## Divergence analysis

What time bins are significantly different from one another?

Because of the weird eyetrackingR synntax, we need to restructure the data slightly so that we can investigate the main effect of AOI. So we instead look at whether the observer was looking into the left or right AOI as a function of where the social image was (left or right).

### Intact condition
```{r}
response_time2 <- make_time_sequence_data(data, time_bin_size = 100,aois = c("isinL","isinR"),summarize_by = "ps",predictor_columns = c("scramb","X3"))

# X3 codes where the social image was.
response_time2$side=factor(response_time2$X3)

# When does the observer look significantly more at the social AOI ? (holm adjustment)
tb_analysis_INT <- analyze_time_bins(data = response_time2[response_time2$scramb==1,],test = "t.test",aoi=c("isinL"),predictor_column =c("side"),  alpha = .05,p_adjust_method = 'holm')
plot(tb_analysis_INT)

summary(tb_analysis_INT)
```

For intact images, the bias for social images is present in every time bin from 100 onwards

### Scrambled condition


```{r}

tb_analysis_SCR <- analyze_time_bins(data = response_time2[response_time2$scramb==2,],test = "t.test",aoi=c("isinL"),predictor_column =c("side"),  alpha = .05,p_adjust_method = 'holm')
plot(tb_analysis_SCR)


summary(tb_analysis_SCR)
```

For scrambled images, the bias for social images is not significant in any time bin after adjusting for multiple comparisons.


### Intact v scrambled condition

```{r}
tb_analysis <- analyze_time_bins(data = response_time,test = "t.test",aoi=c("SOCIAL"),predictor_column =c("scramb"),  alpha = .05,p_adjust_method = 'holm')

plot(tb_analysis, type = "estimate") + theme_light()

summary(tb_analysis)
```

In terms of preference for the social image, intact images diverge from the scrambled images in the time bins 200-1400 ms

*** 

<a id='switching'></a>

## Switching analysis

Divide trials into which AOI participants started on. Calculate swtiches away from this AOI using a rolling wondow
```{r}
onsets <- make_onset_data(data, onset_time = 100, fixation_window_length=100,target_aoi='SOCIAL',distractor_aoi = 'NONSOCIAL')

plot(onsets,predictor_columns="scramb")

onset_switches <- make_switch_data(onsets,predictor_columns = "scramb")

# Visualize subject's switch times
plot(onset_switches,predictor_columns="scramb")

```


Now enter this data into a model


```{r}
model_switches <- lmer(FirstSwitch ~ FirstAOI*scramb + (1 | ps), data=onset_switches, REML=FALSE)
model_switches_p = mixed(FirstSwitch ~ FirstAOI*scramb+(1|ps), onset_switches)
model_switches_p
```


Main effect of First AOI and an interaction bewteen first AOI and scramble. Now unpick the interaction.

```{r}
testInteractions(model_switches, fixed=c("scramb"), pairwise=c("FirstAOI"),adjustment="holm")
```

Observers take longer to switch from the social AOI, but this effect is only significant in the intact condition.

***

<a id='indiff'></a>

## Individual Differences

### Visualise individual data (intact)
```{r}

response_time_mod_in=cbind(response_time[response_time$scramb==1 & !is.na(response_time$Prop),],predict(model_time_sequence_intact3))

colnames(response_time_mod_in)=c(colnames(response_time),"pred")

ggplot(response_time_mod_in[response_time_mod_in$scramb==1,],aes(x=TimeBin,y=Prop))+facet_wrap(~ps,nrow=8)+geom_line(aes(x=TimeBin,y=pred,colour=AOI),size=2,linetype="solid")+geom_point(aes(colour=AOI),size=0.5,shape=6)
```


### Scrambled


```{r}

response_time_mod_sc=cbind(response_time[response_time$scramb==2 & !is.na(response_time$Prop),],predict(model_time_sequence_scramb4))

colnames(response_time_mod_sc)=c(colnames(response_time),"pred")

ggplot(response_time_mod_sc[response_time_mod_sc$scramb==2,],aes(x=TimeBin,y=Prop))+facet_wrap(~ps,nrow=8)+geom_line(aes(x=TimeBin,y=pred,colour=AOI),size=2)+geom_point(aes(colour=AOI),size=0.5,shape=6)
```

### Plot linear and quadratic random effects

```{r}
gh=data.frame()
# Plot fixed effects
getrand=function(model){
for (sub in 1:77){
linear=ranef(model)$ps$ot1[sub]*response_time$ot1[1:50]
quadratic=ranef(model)$ps$ot2[sub]*response_time$ot2[1:50]
modellin=fixef(model)[3]*response_time$ot1[1:50]
modelquad=fixef(model)[4]*response_time$ot2[1:50]
modfull=modellin+modelquad
indfull=linear+quadratic
timebin=response_time$TimeBin[1:50]
gh=data.frame(rbind(cbind(sub,timebin,linear,quadratic,modellin,modelquad,modfull,indfull),gh))
}
  return(gh)
}

curvesIN=getrand(model_time_sequence_intact3)
curvesSC=getrand(model_time_sequence_scramb3)

curvesall=rbind(curvesIN,curvesSC)
curvesall$scramb=rep(c(1,2),each=3850)
curvesall$scramb=factor(curvesall$scramb,levels=c(1,2),labels=c("intact","scrambled"))

ggplot(curvesall,aes(x=timebin,y=indfull))+facet_wrap(~sub,nrow=8)+geom_point(aes(colour=scramb))

```

### Load in the EQ Data

```{r}
EQ_DATA=read.csv('EQ_Data.csv')
EQ=EQ_DATA$EQ.Total
EQS=EQ_DATA$EQ.Social
EQE=EQ_DATA$EQ.Emotion
EQC=EQ_DATA$EQ.Cognitive

library(stringr)

# EQ data doesnt belong to everyone (only 69 people)
EQ_PS=as.numeric(str_extract(EQ_DATA$pps, "[0-9]+"))
```

### Perform a Bootstrapped cluster-based permutation analysis

```{r}

# Define threshold based on alpha = .05 (two tailed)
num_sub = length(unique((EQ_PS)))
threshold_t = qt(p = 1 - .05/2, df = num_sub-1)

response_time_new <- make_time_sequence_data(data, time_bin_size = 100,aois = c("SOCIAL"),predictor_columns = c("scramb"),summarize_by="ps")

response_time_new$EQ=rep(NA,nrow(response_time_new))

# Add EQ data. Here I add the 'Social' subscale (no effects are detected for other sub-scales, or for total EQ score)
for (sub in 1:length(EQ_PS)-1){
  response_time_new[response_time_new$ps==EQ_PS[sub],]$EQ=EQS[sub]
}

# Intact images, look for the effect of EQS in each time bin
df_timeclust_between <- make_time_cluster_data(response_time_new[response_time_new$scramb==1,], test= "lm",predictor_column = "EQ", threshold = threshold_t)

plot(df_timeclust_between) +  ylab("T-Statistic") + theme_light()
```

There are 3 clusters. Perform a bootstrapping analysis to see if these could have been obtained by chance. 

```{r}
clust_analysis_between <- analyze_time_clusters(df_timeclust_between, within_subj = FALSE, samples=1000)

summary(clust_analysis_between)
plot(clust_analysis_between)
```

Only the last cluster is significant after the permutation test. The social component of the EQ predicts enhanced gaze towards the end of the trial 4200ms onwards (p=.047).

As a sanity check, I also applied the same tests for scrambled images and found no effects.

### See whether the random effects for the linear and quadratic terms of the growthcurve model are related to empathy.

```{r}
linear=rep(0,68)
for (sub in 1:length(EQ_PS)-1){
  linear[sub]=ranef(model_time_sequence_intact3)$ps$ot2[sub]
}
```



